\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-29 papers/jfp/3-abstractions.tex
Fix spacing, add a TODO

cloudAck :: Tasks (MonadState Cache) (Integer, Integer) Integer
cloudAck (m, n)
    | m < 0 || n < 0 = Nothing
    | m == 0    = Just $ Task $ const $ pure (n+1)
    | n == 0    = Just $ Task $ \fetch -> fetch (m-1, 1)
    | otherwise = Just $ Task $ \fetch -> do
        cache <- get
        case Map.lookup (m, n) cache of
            Nothing -> do index <- fetch (m, n-1)
                          value <- fetch (m-1, index)
                          modify (Map.insert (m, n) value)
                          return value
            Just value -> return value
\end{minted}
\vspace{1mm}

>>>>

cloudAckermann :: Tasks (MonadState@\,@Cache)@\,@(Integer,@\,@Integer)@\,@Integer
cloudAckermann (m, n)
    | m < 0 || n < 0 = Nothing
    | m == 0    = Just $ Task $ const $ pure (n+1)
    | n == 0    = Just $ Task $ \fetch -> fetch (m-1, 1)
    | otherwise = Just $ Task $ \fetch -> do
        cache <- get
        case Map.lookup (m, n) cache of
            Nothing -> do index <- fetch (m, n-1)
                          value <- fetch (m-1, index)
                          modify (Map.insert (m, n) value)
                          return value
            Just value -> return value
\end{minted}
\vspace{1mm}
